---
title: "Fars Functions"
author: "Richad Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The functions provided will be using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.


## Vignette Info

Two major functions in this package.  `fars_summarize_years` returns a dataframe which summarise the number of accidents during given years.  `fars_map_state` draws a map of a given state number and plots locations of the accidents on given years.  The remaining functions   `make_filename`, `fars_read` and `fars_read_years` are helper functions for the two major functions. `make_filename` return the data file name of an input `year`. `fars_read` reads in data from an input datafile.  `fars_read_years` reads in data of a vector of `year` extract the month and year information and store them in a list. 


## Examples

The numbers of fatal accidents during 2014 is as follows:
```{r}
library(dplyr, quietly = TRUE)
Fars::fars_summarize_years(2014)
```

The following call on fars_map_state draw a map of state Colorado and plots locations of fatal accidents.

```{r}
library(maps)
Fars::fars_map_state(51, 2013)
```
